### 2015-03-11 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Uploaded GC Data

These experiments were conducted at the Delaware County (PA) Emergency Services Training Center (ESTC) in Sharon Hill, PA.

@@

The burn building is a purpose-built live fire training structure comprised of both a two story and three story section. The building is supported with reinforced concrete beams and columns.  The floors and ceilings are also concrete with the interior walls constructed of cement block. The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thinck layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile. The floor of the burn rooms is protected with fire brick.

@@

@@

Additional single thermocouples were installed in conjunction with the bi-directional probes at the exterior vents and in the hallway.  The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm (0.04 in) nominal diameter. Just behind the bead, the thermocouple wire is protected with an 3.2 mm (0.125 in) diameter inconel sheath.  
In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.  In the hallway, there were seven thermocouples positioned vertically at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft)   In the south window opening, there were four thermocouples are located 0.28 m (0.95 ft), 0.58 (1.90 ft), 0.84 m (2.85 ft), and 1.16 m (3.8 ft) below the soffit.

>>>>

These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.

@@

The burn building is a purpose-built live fire training structure comprised of both a two story and three story section. The building is supported with reinforced concrete beams and columns.  The floors and ceilings are also concrete with the interior walls constructed of cement block. The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thick layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile. The floor of the burn rooms is protected with fire brick.

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
	\caption{Instrumentation Legend}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

Additional single thermocouples were installed in conjunction with the bi-directional probes at the exterior vents and in the hallway.  The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm (0.04 in) nominal diameter. Just behind the bead, the thermocouple wire is protected with an 3.2 mm (0.125 in) diameter inconnel sheath.  
In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.  In the hallway, there were seven thermocouples positioned vertically at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft)   In the south window opening, there were four thermocouples are located 0.28 m (0.95 ft), 0.58 (1.90 ft), 0.84 m (2.85 ft), and 1.16 m (3.8 ft) below the soffit.
